Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-05-16 article-models-ttinternal.tex
small improvements

\begin{defn}
An extension algebra homomorphism from $(A,P,\epsilon_0,\epsilon_1)$ to
$(B,Q,\eta_0,\eta_1)$ in context $\Gamma$ is a pair $(f_0,f_1)$ consisting of
\begin{align*}
\jhom*{\Gamma}{A}{B}{f_0}
  \\
\jfhom*{\Gamma}{A}{B}{f_0}{P}{Q}{f_1}
\end{align*}
for which the diagrams
\begin{equation}\label{eq:extalg-hom1}
\begin{tikzcd}
\ctxext{A}{P}
  \ar{r}{\jvcomp{}{f_0}{f_1}}
  \ar{d}[swap]{\epsilon_0}
& \ctxext{B}{Q}
  \ar{d}{\eta_0}
  \\
A
  \ar{r}[swap]{f_0}
& B
\end{tikzcd}
\end{equation}
and
\begin{equation}\label{eq:extalg-hom2}
\begin{tikzcd}[column sep=large]
\ctxext{P}{\jcomp{}{\epsilon_0}{P}}
  \ar{r}{\jvcomp{}{f_1}{\jcomp{}{\epsilon_0}{f_1}}}
  \ar{d}[swap]{\epsilon_1}
& \jcomp{}{f_0}{\ctxext{Q}{\jcomp{}{\eta_0}{Q}}}
  \ar{d}{\jcomp{}{f_0}{\eta_1}}
  \\
P
  \ar{r}[swap]{f_1}
& \jcomp{}{f_0}{Q}
\end{tikzcd}
\end{equation}
commute judgmentally.
\end{defn}

>>>>

\begin{defn}
An \emph{extension homomorphism} from $(A,P,\epsilon_0,\epsilon_1)$ to
$(B,Q,\eta_0,\eta_1)$ in context $\Gamma$ is a pair $(f_0,f_1)$ consisting of
\begin{align*}
\jhom*{\Gamma}{A}{B}{f_0}
  \\
\jfhom*{\Gamma}{A}{B}{f_0}{P}{Q}{f_1}
\end{align*}
for which the diagrams
\begin{equation}\label{eq:extalg-hom1}
\begin{tikzcd}
\ctxext{A}{P}
  \ar{r}{\jvcomp{}{f_0}{f_1}}
  \ar{d}[swap]{\epsilon_0}
& \ctxext{B}{Q}
  \ar{d}{\eta_0}
  \\
A
  \ar{r}[swap]{f_0}
& B
\end{tikzcd}
\end{equation}
and
\begin{equation}\label{eq:extalg-hom2}
\begin{tikzcd}[column sep=large]
\ctxext{P}{\jcomp{}{\epsilon_0}{P}}
  \ar{r}{\jvcomp{}{f_1}{\jcomp{}{\epsilon_0}{f_1}}}
  \ar{d}[swap]{\epsilon_1}
& \jcomp{}{f_0}{\ctxext{Q}{\jcomp{}{\eta_0}{Q}}}
  \ar{d}{\jcomp{}{f_0}{\eta_1}}
  \\
P
  \ar{r}[swap]{f_1}
& \jcomp{}{f_0}{Q}
\end{tikzcd}
\end{equation}
commute judgmentally.
\end{defn}
